Higher order unification for free!

### 2024-04-08 paper/main.tex
tex: fidelity linketa

@@

\begin{lemma}
  Given a \hoUnifPb and a substitution $\sigma$ then the resolution of
  $\sigma\hoUnifPb$ guarantees \cref{prop:fidelity} 
\end{lemma}

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by
  \cref{def:progBetaLL,def:progBetaRH}, then \linkbeta disappear and the
  unification done between terms in \llambda. This problem unifies iff
  its corresponding \Fo{} problem unifies too. If $\sigma\hoUnifPb$ is in \notllambda,
  then, by \cref{lemma:keep-fidelity}, the unification fails, as per the
  corresponding unification in \Fo{}.
\end{proof}

>>>>

\begin{lemma}[Fidelity with \linketa]
  Let \hoUnifPb a unification problem and $\sigma$ a substitution. The introduction 
  of \linketa guarantees \cref{prop:fidelity} 
  \label{lemma:fidelity-maybeeta}
\end{lemma}

\begin{proof}[Proof sketch]
  If 1) a \linketa is activated by \progressetaleft, then unification is done
  between a \maybeeta term $t_1$ and a term $t_2$ (with $\wellb(t_2)$). This
  activation performs a unification which succeeds iff the original problem in
  \Fo{} succeeds. If 2) a \linketa is activated by \progressetadedup, then the
  unification is done between two \maybeeta terms, and again this unification
  succeeds iff it succeeds in \Fo{}. Finally, if 3) a \linketa is activated by
  \progressetaright, the unification, done between a variable and a term,
  always succeeds, this is what we expect to guarantee fidelity, since we
  are essentially removing a hole added by the compilation in the place of a
  \maybeeta subterm. In all the cases fidelity is respected.
\end{proof}

@@

\begin{lemma}[Fidelity with \linkbeta]
  The introduction of \linkbeta guarantees \cref{prop:fidelity} 
\end{lemma}

\begin{proof}[Proof sketch]
  Let \hoUnifPb a unification problem and $\sigma$ a substitution
  such that $\hoUnifPb \in \notllambda$. 
  If $\sigma\hoUnifPb$ is in \llambda, then by
  \cref{def:progBetaLL,def:progBetaRH}, the \linkbeta associated to the subterm of
  \hoUnifPb have been solved and removed. The
  unification is done between terms in \llambda and by \cref{lemma:fidelity-maybeeta}
  fidelity is guaranteed. If $\sigma\hoUnifPb$ is in \notllambda,
  then, by \cref{lemma:keep-fidelity}, the unification fails, as per the
  corresponding unification in \Fo{}.
\end{proof}
